Excuse me, do you have a moment to talk about version control?

### 2017-05-13 README.Rmd
More on issues
Kill 'special features of github' section

GitHub __issues__ are another powerful feature of the platform. Recall that we are repurposing Git, a tool designed to facilitate software development. The issues for a project are its bug tracker. For projects that are not pure software development, we use this machinery to organize our to do list more generally. The basic unit is an issue and you can interact with them in two ways. First, issues are integrated into the project's web interface on GitHub, with a rich set of options for linking to project files and incremental changes. Second, issues and their associated comment threads appear in your email, just like regular messages (this can, of course, be configured). The result is that all correspondence about a project comes through your normal channels, but is also tracked inside the project itself, with excellent navigability and search capabilities.

@@

## Don't get caught up on these things

@@

@@

## Special features of GitHub

*at this point, just fodder mined from various locations in Happy Git*

 * **Pull requests.** Git allows a project to have multiple, independent branches of development, with the notion that some should eventually be merged back into the main development branch. These are technical Git terms but hopefully also make sense on their own. A pull request is a formal proposal that says: "Here are some changes I would like to make." It might be linked to a specific issue: "Related to #14." or "Fixes #56". GitHub facilitates and preserves the discussion of the proposal, holistically and line-by-line.

>>>>

GitHub __issues__ are another powerful feature of the platform. Recall that we are repurposing Git, a tool designed to facilitate software development. The issues for a project are its bug tracker. For projects that are not pure software development, we use this machinery to organize our to do list more generally. The basic unit is an issue and you can interact with them in two ways.

First, issues are integrated into the project's web interface on GitHub, with a rich set of options for linking to project files and incremental changes. Second, issues and their associated comment threads appear in your email, just like regular messages (this can, of course, be configured). The result is that all correspondence about a project comes through your normal channels, but is also tracked inside the project itself, with excellent navigability and search capabilities. For software, issues are used to track bugs and feature requests. In a data analysis project, you might open an issue for a specific sub-analysis or complicated figure that needs to be made. In a course, we use them to manage homework submission, marking, and peer review.

@@

## Things you can tackle later

@@

*text pulled from elsewhere but might fit here?* **Pull requests.** Git allows a project to have multiple, independent branches of development, with the notion that some should eventually be merged back into the main development branch. These are technical Git terms but hopefully also make sense on their own. A pull request is a formal proposal that says: "Here are some changes I would like to make." It might be linked to a specific issue: "Related to #14." or "Fixes #56". GitHub facilitates and preserves the discussion of the proposal, holistically and line-by-line.

@@
